\documentclass[12pt]{article}

\usepackage{answers}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{mathrsfs}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{circuitikz} % PACKAGE for circuit desing
 % http://texdoc.net/texmf-dist/doc/latex/circuitikz/circuitikzmanual.pdf
\usepackage{imakeidx} %for generating the index file

% short command section: use \N to generate the \mathbb{N} command
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\B}{\textbf}
\newcommand{\I}{\textit}
\newcommand{\bite}{\begin{itemize}} %Begin ITEmize
\newcommand{\fite}{\end{itemize}}   %Finisch ITEmize


\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\csch}{csch}
 
\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{definition}[2][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{proposition}[2][Proposition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{solution}[2][Solution]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
 
 \makeindex
 
\begin{document}
 
% --------------------------------------------------------------
%                         Start here
% --------------------------------------------------------------
 
\title{Introduction to Electronics\\
Formulas and utilities}
\author{Tommaso Polloni\\
and }
 
 The very first idea is to make this document a learning tool for git, latex and, of course, of Electronics. I will be very proud of ourselves if we reach to maintain English as its primary language.
\maketitle
\tableofcontents

\section{Semiconductors} \index{Semiconductors}
Semiconductors are material with an electrical conductivity value falling between that of a conductor and an insulator.
An important property of semiconductors is that, during a temperature increment, their resistance decreases.
Common semiconductors material are:
\begin{itemize}
	\item \index{Silicon}Silicon, Si. Z (i.e. atomic number) = 14. IV ($14^{th}$) group.
	\item Germanium, Ge. Atomic number = 32. IV ($14^{th}$) group
	\item Gallium Arsenide, GaAs, a compound of Gallium and Arsenic.
\end{itemize}

\subsection{Semiconductors: a nuclear approach}
A neutral Silicon atom possesses 14 protons and many electrons.
\begin{itemize}
	\item the first 10 of them lies in the first energy level: they fit perfectly around the nucleus and  are not involved in chemical reactions or anything (because very high energy is necessary to interact with them).
	\item the remaining 4 electrons are called \textit{valence electrons}\index{valence electrons} and are at higher energy levels. They are involved in the \textit{covalent bond}.
\end{itemize}
When temperature is near at the absolute zero ($-273^o C$) the Silicon atoms assume a crystal form in which every \textit{valence electron} is shared with the nearest 4 atoms of Silicon, with a covalent bond: in this circumstance Silicon act as an \textbf{insulator}.
At higher temperatures, the atoms get energy from the outside: \textbf{1 eV} is the energy amount necessary for breaking a covalent bond. 
\subsubsection{Electrons and Holes}
When the break happens, an electron \I{jumps} to valence band and a hole is generated (note that the semiconductor remains neutral). Remember that the hole is in fact the absence of an electron, and it may be referred to as a \B{cation}, an atom with positive charge. 
\subsubsection{Valence and conduction bands}
Without the necessary energy, electrons remain under the \I{Fermi level}, in a zone called \I{Valence Band}; when the \I{jump} occurs, electrons step over the \I{Fermi level} and stay in the \I{conduction band}. In the conduction band charge carrier have less constraints and can easily move in the crystalline lattice, depending on the intensity of the electro-magnetic field.
\subsubsection{Silicon properties}
\bite
	\item To complete \index{TO DO}
	\item It is compatible with $SiO_2$ and $Al$
\fite

\subsection{Doping}
The doping process consists in significantly change the number of \textit{electrons }or \textit{holes} in a semiconductor.
This result is achieved inserting atoms of the doping element in the crystalline arrangement of the doped.
\subsubsection{Utilities and numbers}
\begin{itemize}
	\item $N_{d} \approxeq 10^{12} : 10^{20} cm^{-3}$ number of donors
	\item $p 	[\dfrac{electrons}{cm^3}]$ number of holes 
	\item $n 	[\dfrac{electrons}{cm^3}]$ number of electrons 
\end{itemize}

TO ADD: the part regarding mobility and resistance.

\section{Diodes}
Diodes are defined as a p-n junction.
\begin{circuitikz}2
	\draw (0,0) to[Do, l=$Diode$, i>^=$i$, v = $v$] (2,0);3
\end{circuitikz}
Is is made by two parts: the left part (according to the figure) is a p-doped semiconductor in which there are holes left.
The other part, on the contrary, is n-doped in which there are electrons left. 

% --------------------------------------------------------------
%                         Sample structures
% --------------------------------------------------------------


\newpage
%Below is an example of the problem environment
\begin{problem}{6}
\begin{enumerate}[label=\alph*)]
    \item Suppose an entire function $f$ is bounded by $M$ along $|z|=R$. Show that the coefficients $C_k$ in its power series expansion about $0$ satisfy
    \[
    |C_k|\leq\frac{M}{R^k}.
    \]
    \item Suppose a polynomial is bounded by $1$ in the unit disc. Show that all its coefficients are bounded by 1.
\end{enumerate}
\end{problem}

%Below is the solution environment
\begin{solution}{}
Part a): Since $f$ is an entire function it can be expressed as an infinite power series, i.e.
\[
f(z)=\sum_{k=0}^\infty\frac{f^{(k)}(0)}{k!}z^k=\sum_{k=0}^\infty C_kz^k.
\]
If we recall Cauchy's Integral we have
\[
f(z)=\frac{1}{2\pi i}\int_\gamma\frac{f(w)}{w-z}\ dw,
\]
carefully notice that $\frac{1}{w-z}=\frac{1}{w}\cdot\frac{1}{1-\frac{z}{w}}$ can be written as a geometric series. We have

%The align environment with no label
\begin{align*}
\frac{1}{2\pi i}\int_\gamma\frac{f(w)}{w-z}\ dw &=\frac{1}{2\pi i}\int_\gamma\left\lbrace\frac{f(w)}{w}\cdot\left(\frac{1}{1-\frac{z}{w}}\right) \right\rbrace\ dw\\[8pt]
&=\frac{1}{2\pi i}\int_\gamma\left\lbrace\frac{f(w)}{w}\cdot\left(1+\frac{z}{w}+\frac{z^2}{w^2}+\frac{z^3}{w^3}+\cdots\right) \right\rbrace\ dw\\[8pt]
&=\left(\frac{1}{2\pi i}\int_\gamma \frac{f(w)}{w}\ dw\right)z^0+\left(\frac{1}{2\pi i}\int_\gamma \frac{f(w)}{w^2}\ dw\right)z^1+\left(\frac{1}{2\pi i}\int_\gamma \frac{f(w)}{w^3}\ dw\right)z^2\cdots
\end{align*}
Now take the modulus of $C_k$ to get
\[
|C_k|=\left\lvert\frac{1}{2\pi i}\int_\gamma \frac{f(w)}{w^{k+1}}\ dw \right\rvert\leq\frac{1}{2\pi}\int_\gamma\frac{|f(w)|}{|w^{k+1}|}\ |dw|\leq \frac{M}{2\pi}\int_\gamma\frac{|dw|}{|w^{k+1}|}
\]
Then integrate along $\gamma(\theta)=Re^{i\theta}$ for $\theta\in [0,2\pi]$ to get
\[
|C_k|\leq \frac{M}{2\pi}\int_0^{2\pi}\frac{|iRe^{i\theta}\ d\theta|}{|R^{k+1}e^{ik\theta}|}=\frac{M}{2\pi\cdot R^k}\int_0^{2\pi}\ d\theta=\frac{M}{R^k}.
\]
Hence, $|C_k|\leq \frac{M}{R^k}$.
\end{solution}
\pagebreak



\printindex

\end{document}
